---
title: "Plot1"
author: "Abraam Gergis"
date: "October 20, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction:

  This assignment uses data from the UC Irvine Machine Learning Repository, a popular repository for machine learning datasets. In particular, we will be using the "Individual household electric power consumption Data Set". Measurements of electric power consumption in one household with a one-minute sampling rate over a period of almost 4 years. Different electrical quantities and some sub-metering values are available.
  
## Goal of assignment:

  Our overall goal here is simply to examine how household energy usage varies over a 2-day period in February, 2007. Your task is to reconstruct these plots, all of which were constructed using the base plotting system.
  
## Loading the data:

```{r}
setwd("~/Exploratory Data Analysis")

colNames <- names(read.table("~/Exploratory Data Analysis/household_power_consumption.txt", nrow=1, header=TRUE, sep=";"))

pwercon <- read.table("~/Exploratory Data Analysis/household_power_consumption.txt", na.strings = "?", skip = grep("^[1,2]/2/2007", readLines("~/Exploratory Data Analysis/household_power_consumption.txt"))-1, nrow = 2879, sep = ";", header = FALSE, col.names = colNames)
```

## Processing the data:

```{r}
library(lubridate)
pwercon$Date <- mdy(pwercon$Date)
```

## Creating the first plot:

```{r}
library(ggplot2)

png(filename = "plot1.png", width = 480, height = 480)

g1 <- ggplot(data = pwercon, aes(Global_active_power))

g1 + geom_histogram(bins = 20, fill = "red", color = "black") + labs(x = "Global Active Power (kilowatts)", y = "Frequency", title ="Global Active Power")

dev.off()
```
